### 2018-12-29 code.tex
typos fixed

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{graphics/fig_HM_to_DD_pairs_dist_separ.png}
    \caption[Inter-arrival distance separation of H-M pairs to D-D pairs into the RECAT scheme]{Inter-arrival distance separation after re-categorisation of H-H pairs ti D-D pairs into the RECAT scheme.}
    \label{fig:HM_to_DD_pairs_dist_separ}
\end{figure}

\chapter{BIKF Schemati}

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{graphics/fig_HM_to_DD_pairs_dist_separ.png}
    \caption[Inter-arrival distance separation of H-M pairs to D-D pairs into the RECAT scheme]{Inter-arrival distance separation after re-categorisation of H-H pairs to D-D pairs into the RECAT scheme.}
    \label{fig:HM_to_DD_pairs_dist_separ}
\end{figure}

\chapter{BIKF Schematic}
